---
title: "2-16 Clean Data for Visuals"
author: "Adam Sneath"
date: "February 14, 2019"
output: pdf_document
---

## Filter the data to individual .csv files for C12, C14, C15, C17, C20
### Use as a template for filtering to any specific measure(s)
### Note for Pitt students: All .csv files will be uploaded to the box folder "Data (see README)" for access on your own device or generally in R Studio 

### The measures are defined as follows: 

#### DMD15: Statin Use in Persons with Diabetes - The percentage of Members age 40-75 who were dispensed a medication for diabetes that receive a statin medication. 

#### C12: Osteoporosis Management in Women Who Had a Fracture - The percentage of female Members age 67 - 85 who suffered a fracture and who had either a bone mineral density (BMD) test or prescription for a drug to treat or prevent osteoporosis in the six months after the fracture. 

#### C14: Comprehensive Diabetes Care: Medical Attention for Nephropathy (kidney damage) - The percentage of diabetic Members age 18 - 75 who had medical attention for nephropathy.

#### C15: Comprehensive Diabetes Care: HbA1c Control (<=9%) - The percentage of Members age 18 - 75 with diabetes (type 1 or type 2) whose most recent Hemoglobin A1C is <=9.0%. 

#### C17: Disease-Modifying Anti-Rheumatic Drug Therapy for Rheumatoid Arthritis - The percentage of Members age 18 and older who were diagnosed with rheumatoid arthritis and who were dispensed at least one ambulatory prescription for a disease-modifying anti-rheumatic drug (DMARD). 

#### C20: Medication Reconciliation Post-Discharge - The percentage of discharges from January 1-December 1 of the measurement year for Members 18 years of age and older for whom medications were reconciled the date of discharge through 30 days after discharge (31 total days). 

#### All other measures are defined in the Dashboard code :)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stringr)
library(sas7bdat)
library(ggplot2)
library(ggmap)
library(readxl)
knitr::opts_chunk$set(echo = TRUE)
options(stringsAsFactors = FALSE)
prac <- read.csv("C:/Users/adsne/Desktop/2019 Spring/Healthcare/Project/18-Feb-19_practice_geocoded.csv")
zip_inc <- read_excel("C:/Users/adsne/Desktop/2019 Spring/Healthcare/Project/2006-2010_US_income_by_zip_UMICH.xlsx")
```

```{r Find Missing Zips}
setdiff(prac$Zip,zip_inc$Zip)
#This was corrected manually in excel, so now there's no more missing zips
```

```{r Join Household Income Data to practice Data by Zipcode}
colnames(prac)[89] <- "Zip"
#Calling the practice data, with income values added "fin"
fin <- left_join(prac,zip_inc,by="Zip")
#Fix id's to be like original (either read or write csv functions dropped the leading 0s somewhere)
fin$practice_id2 <- str_pad(fin$practice_id2,9,"left","0")
names(prac)
```

```{r Filter Data to Underperforming Measures and Ditch ZERO or NA Denominators}

#Bad Measures (Stars <= 3)
C12 <- fin %>% filter(measure_ds == "C12: Osteoporosis Management in Women who had a Fracture")
C14 <- fin %>% filter(measure_ds == "C14: Comprehensive Diabetes Care: Medical Attention for Nephropathy")
C15 <- fin %>% filter(measure_ds == "C15: Comprehensive Diabetes Care: HbA1c Control (<=9%)")
C17 <- fin %>% filter(measure_ds == "C17: Disease Modifying Anti-Rheumatic Drug Therapy for Rheumatoid Arthritis")
C20 <- fin %>% filter(measure_ds == "C20: Medication Reconciliation Post-Discharge")
C21 <- fin %>% filter(measure_ds == "C21: All-cause Readmissions")
DMD15 <- fin %>% filter(measure_ds == "DMD15: Statin Use in Persons with Diabetes")

#OK Measures (Stars = 4)
C01 <- fin %>% filter(measure_ds == "C01: Breast Cancer Screening")
C02 <- fin %>% filter(measure_ds == "C02: Colorectal Cancer Screening")
C07 <- fin %>% filter(measure_ds == "C07: Adult BMI Assessment")
C13 <- fin %>% filter(measure_ds == "C13: Comprehensive Diabetes Care: Eye Exam (retinal) performed")
D11 <- fin %>% filter(measure_ds == "D11: Medication Adherence for Diabetes Medications")
D13 <- fin %>% filter(measure_ds == "D13: Medication Adherence for Cholesterol (Statins)")
DMC17 <- fin %>% filter(measure_ds == "DMC17: Statin Therapy for Patients with Cardiovascular Disease")

#Good Measures (Stars = 5)
D12 <- fin %>% filter(measure_ds == "D12: Medication Adherence for Hypertension: RASA")
D14 <- fin %>% filter(measure_ds == "D14: Medication Therapy Management")

#Check for NA Denominator
# length(which(is.na(C12$denominator)))
# length(which(is.na(C14$denominator)))
# length(which(is.na(C15$denominator)))
# length(which(is.na(C17$denominator)))
#########C20 has NA denominators#################
C20 <- C20 %>% filter(is.na(denominator) == FALSE)
# length(which(is.na(C20$denominator)))
# length(which(is.na(DMD15$denominator)))
# length(which(is.na(C01$denominator)))
# length(which(is.na(C02$denominator)))
# length(which(is.na(C07$denominator)))
# length(which(is.na(C13$denominator)))
#########C21 has NA denominators#################
C21 <- C21 %>% filter(is.na(denominator) == FALSE)
# length(which(is.na(C21$denominator)))
# length(which(is.na(D11$denominator)))
# length(which(is.na(D13$denominator)))
# length(which(is.na(DMC17$denominator)))
# length(which(is.na(D12$denominator)))
#########D14 has NA denominators#################
D14 <- D14 %>% filter(is.na(denominator) == FALSE)
# length(which(is.na(D14$denominator)))

#Filter out ZERO denominators
C12 <- C12 %>% filter(denominator != 0)
C14 <- C14 %>% filter(denominator != 0) 
C15 <- C15 %>% filter(denominator != 0) 
C17 <- C17 %>% filter(denominator != 0)
C20 <- C20 %>% filter(denominator != 0)
DMD15 <- DMD15 %>% filter(denominator != 0)
C01 <- C01 %>% filter(denominator != 0)
C02 <- C02 %>% filter(denominator != 0)
C07 <- C07 %>% filter(denominator != 0)
C13 <- C13 %>% filter(denominator != 0)
D11 <- D11 %>% filter(denominator != 0)
D13 <- D13 %>% filter(denominator != 0)
DMC17 <- DMC17 %>% filter(denominator != 0)
D12 <- D12 %>% filter(denominator != 0)
D14 <- D14 %>% filter(denominator != 0)

###### All of these equal zero which is good #####
# length(which(is.na(C12$compliance)))
# length(which(is.na(C14$compliance)))
# length(which(is.na(C15$compliance)))
# length(which(is.na(C17$compliance)))
# length(which(is.na(C20$compliance)))
# length(which(is.na(DMD15$compliance)))
# length(which(is.na(C01$compliance)))
# length(which(is.na(C02$compliance)))
# length(which(is.na(C07$compliance)))
# length(which(is.na(C13$compliance)))
# length(which(is.na(D11$compliance)))
# length(which(is.na(D13$compliance)))
# length(which(is.na(DMC17$compliance)))
# length(which(is.na(D12$compliance)))
# length(which(is.na(D14$compliance)))

#names(DMD15)
```


```{r Trim All To Relevant Columns and Rename}

#names(C12)

C12 <- C12[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C12) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C14 <- C14[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C14) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C15 <- C15[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C15) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C17 <- C17[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C17) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C20 <- C20[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C20) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

DMD15 <- DMD15[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(DMD15) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C01 <- C01[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C01) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C02 <- C02[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C02) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C07 <- C07[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C07) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C13 <- C13[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C13) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C21 <- C21[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C21) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

D11 <- D11[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(D11) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

D12 <- D12[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(D12) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

D13 <- D13[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(D13) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

D14 <- D14[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(D14) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

DMC17 <- DMC17[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,21,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(DMC17) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Star_Rating","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

```

```{r}
write.csv(C12, file="C12.csv", row.names = FALSE)
write.csv(C14, file="C14.csv", row.names = FALSE)
write.csv(C15, file="C15.csv", row.names = FALSE)
write.csv(C17, file="C17.csv", row.names = FALSE)
write.csv(C20, file="C20.csv", row.names = FALSE)
write.csv(DMD15, file="DMD15.csv", row.names = FALSE)
write.csv(C01, file="C01.csv", row.names = FALSE)
write.csv(C02, file="C02.csv", row.names = FALSE)
write.csv(C07, file="C07.csv", row.names = FALSE)
write.csv(C13, file="C13.csv", row.names = FALSE)
write.csv(C21, file="C21.csv", row.names = FALSE)
write.csv(D11, file="D11.csv", row.names = FALSE)
write.csv(D12, file="D12.csv", row.names = FALSE)
write.csv(D13, file="D13.csv", row.names = FALSE)
write.csv(D14, file="D14.csv", row.names = FALSE)
write.csv(DMC17, file="DMC17.csv", row.names = FALSE)
```

```{r Rank Measure-Specific Compliance By City}
##DMD15

test1 <- DMD15 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits1 <- unique(test1$City)

temp1 <- c()
for(i in 1:length(bits1)){
  bit <- test1 %>% filter(City == bits1[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp1 <- append(temp1,new)
}

test1$City.Rank <- temp1 

##C12

test2 <- C12 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)
test2

bits2 <- unique(test2$City)

temp2 <- c()
for(i in 1:length(bits2)){
  bit <- test2 %>% filter(City == bits2[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp2 <- append(temp2,new)
}

test2$City.Rank <- temp2
test2

##C14

test3 <- C14 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits3 <- unique(test3$City)

temp3 <- c()
for(i in 1:length(bits3)){
  bit <- test3 %>% filter(City == bits3[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp3 <- append(temp3,new)
}

test3$City.Rank <- temp3

##C15

test4 <- C15 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits4 <- unique(test4$City)

temp4 <- c()
for(i in 1:length(bits4)){
  bit <- test4 %>% filter(City == bits4[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp4 <- append(temp4,new)
}

test4$City.Rank <- temp4

##C17

test5 <- C17 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits5 <- unique(test5$City)

temp5 <- c()
for(i in 1:length(bits5)){
  bit <- test5 %>% filter(City == bits5[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp5 <- append(temp5,new)
}

test5$City.Rank <- temp5

##C20

test6 <- C20 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits6 <- unique(test6$City)

temp6 <- c()
for(i in 1:length(bits6)){
  bit <- test6 %>% filter(City == bits6[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp6 <- append(temp6,new)
}

test6$City.Rank <- temp6

##C01

test7 <- C01 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits7 <- unique(test7$City)

temp7 <- c()
for(i in 1:length(bits7)){
  bit <- test7 %>% filter(City == bits7[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp7 <- append(temp7,new)
}

test7$City.Rank <- temp7

##C02

test8 <- C02 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits8 <- unique(test8$City)

temp8 <- c()
for(i in 1:length(bits8)){
  bit <- test8 %>% filter(City == bits8[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp8 <- append(temp8,new)
}

test8$City.Rank <- temp8

##C07

test9 <- C07 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits9 <- unique(test9$City)

temp9 <- c()
for(i in 1:length(bits9)){
  bit <- test9 %>% filter(City == bits9[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp9 <- append(temp9,new)
}

test9$City.Rank <- temp9

##C13

test10 <- C13 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits10 <- unique(test10$City)

temp10 <- c()
for(i in 1:length(bits10)){
  bit <- test10 %>% filter(City == bits10[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp10 <- append(temp10,new)
}

test10$City.Rank <- temp10

##C21

test11 <- C21 %>% filter(Denominator >= 2) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits11 <- unique(test11$City)

temp11 <- c()
for(i in 1:length(bits11)){
  bit <- test11 %>% filter(City == bits11[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp11<- append(temp11,new)
}

test11$City.Rank <- temp11

##D11

test12 <- D11 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits12 <- unique(test12$City)

temp12 <- c()
for(i in 1:length(bits12)){
  bit <- test12 %>% filter(City == bits12[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp12 <- append(temp12,new)
}

test12$City.Rank <- temp12

##D12

test13 <- D12 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits13 <- unique(test13$City)

temp13 <- c()
for(i in 1:length(bits13)){
  bit <- test13 %>% filter(City == bits13[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp13<- append(temp13,new)
}

test13$City.Rank <- temp13

##D13

test14 <- D13 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits14 <- unique(test14$City)

temp14 <- c()
for(i in 1:length(bits14)){
  bit <- test14 %>% filter(City == bits14[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp14<- append(temp14,new)
}

test14$City.Rank <- temp14

##D14

test15 <- D14 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits15 <- unique(test15$City)

temp15 <- c()
for(i in 1:length(bits15)){
  bit <- test15 %>% filter(City == bits15[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp15<- append(temp15,new)
}

test15$City.Rank <- temp15

##DMC17

test16 <- DMC17 %>% filter(Denominator >= 3) %>% group_by(City) %>% select(City,Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Star_Rating,Address,Needed4,Needed5,Numerator,Program,Stars_Par) %>% arrange(City)

bits16 <- unique(test16$City)

temp16 <- c()
for(i in 1:length(bits16)){
  bit <- test16 %>% filter(City == bits16[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp16<- append(temp16,new)
}

test16$City.Rank <- temp16

```

```{r Reorder Columns}

names(test8)

test1 <- test1[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test2 <- test2[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test3 <- test3[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test4 <- test4[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test5 <- test5[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test6 <- test6[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test7 <- test7[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test8 <- test8[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test9 <- test9[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test10 <- test10[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test11 <- test11[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test12 <- test12[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test13 <- test13[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test14 <- test14[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test15 <- test15[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]
test16 <- test16[,c(1,2,13,3,6,10,4,8,9,5,7,11,12)]

```

```{r Export to .csv}

write.csv(test2, file="C12Ranked.csv", row.names = FALSE)
write.csv(test3, file="C14Ranked.csv", row.names = FALSE)
write.csv(test4, file="C15Ranked.csv", row.names = FALSE)
write.csv(test5, file="C17Ranked.csv", row.names = FALSE)
write.csv(test6, file="C20Ranked.csv", row.names = FALSE)
write.csv(test1, file="DMD15Ranked.csv", row.names = FALSE)
write.csv(test7, file="C01Ranked.csv", row.names = FALSE)
write.csv(test8, file="C02Ranked.csv", row.names = FALSE)
write.csv(test9, file="C07Ranked.csv", row.names = FALSE)
write.csv(test10, file="C13Ranked.csv", row.names = FALSE)
write.csv(test11, file="C21Ranked.csv", row.names = FALSE)
write.csv(test12, file="D11Ranked.csv", row.names = FALSE)
write.csv(test13, file="D12Ranked.csv", row.names = FALSE)
write.csv(test14, file="D13Ranked.csv", row.names = FALSE)
write.csv(test15, file="D14Ranked.csv", row.names = FALSE)
write.csv(test16, file="DMC17Ranked.csv", row.names = FALSE)

```